Local to global N input modelling

### 2025-05-27 08_manuscript/_manuscript/manuscript.qmd
MS to use new data

affiliations:
  - id: 1
    name: Institute for Marine and Antarctic Studies
    group: Fisheries & Aquaculture
    address: 29 Nubeena Crescent
    city: Taroona
    region: TAS
    country: Australia
    postal-code: 7053
    url: https://www.imas.utas.edu.au/
  - id: 2
    name: Centre for Marine Socioecology
    url: https://marinesocioecology.org/
  - id: 1
    name: Institute for Marine and Antarctic Studies
    group: Ecology & Biodiversity
    # address: 29 Nubeena Crescent
    # city: Taroona
    # region: TAS
    # country: Australia
    # postal-code: 7053
    url: https://www.imas.utas.edu.au/
  # - id: 3
  #   name: Heriott-Watt University, Institute for Life and Earth Sciences
  #   department: School of Energy, Geoscience, Infrastructure and Society
  #   address: Franklin Road
  #   city: Stromness
  #   region: Orkney
  #   country: United Kingdom
  #   postal-code: KW16 3AN
  #   url: https://www.hw.ac.uk/
# keywords:
#   - keyword
#   - keyword
# abstract: |
#   Any new aquaculture venture...
# plain-language-summary: |
#   Plain language summary goes here....
# key-points:
#   - Point 1
#   - Point 2
bibliography: ["../resources/refs.bib", "../resources/manual-refs.bib"]

format: 
  html:
    theme: simplex
    css: ["../resources/extra.css"]
    code-fold: true
    code-overflow: wrap
    toc: true
    toc-expand: true
    toc-location: left
    lang: en-GB
    grid:
      sidebar-width: 350px
      body-width: 1200px
      margin-width: 250px
      gutter-width: 2em
  # pdf:
  #   papersize: a4
  #   linestretch: 1.15
  #   link-citations: true
  #   keep-tex: true
  #   template-partials:
  #     - "../resources/title.tex"
  #   include-in-header:
  #     file: "../resources/header_extra.tex"

@@

```{r setup}
#| include: false
#| cache: false
#| eval: true

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(dtplyr)
library(furrr)
library(RColorBrewer)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()
```

@@

# Output paths
output_farm_data_path <- here() %>% file.path("outputs", "farm_data")
output_species_data_path <- here() %>% file.path("outputs", "species_data")
output_sens_data_path <- here() %>% file.path("outputs", "sensitivity_data")
output_farm_growth_data_path <- here() %>% file.path("outputs", "farm_growth_data")
output_cohort_growth_data_path <- here() %>% file.path("outputs", "cohort_growth_data")

@@

@@

```{r farm temperature data}
farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread()
farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
  rename(farm_ID = farm_id)

@@

overall_mean <- mean(farm_temp_means$mean_temp)
overall_sd <- sd(farm_temp_means$mean_temp)
```

Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD)

```{r fig-farm-mean-temps}
#| fig-cap: Options for showingf arm site mean temperatures. (Top left) Mean temperature by latitude across countries. (Top right) Distribution of mean temperatures by hemisphere. (Bottom) Global distribution of mean temperatures.
#| fig-height: 6
#| fig-width: 6

@@

* Farms with a mean temperature of $\leq 6^\circ$C were excluded - a total of `r as.integer(length(farms_to_omit))` farms.

@@

```{r fig-cohorts}
#| fig-cap: Example of cohorts

@@

@@

Parameter sensitivity was tested by varying each parameter in Table @tbl-params by $\pm 10$% and calculating sensitivity as:

@@

sens_data %>% 
  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
  geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
  labs(x = "Adjusted parameter", y = "Sensitivity") +
  theme_classic() + 
  theme(legend.position = "none", 
        strip.text = element_blank(), 
        aspect.ratio = 0.8,
        text = element_text(size = 12),
        axis.title.y = element_blank()) +
  coord_flip()
```

@@

@@

* Main point is the difference between feeds. 
* This should be expressed in t/t salmon, so farm biomass is also important.
* Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)

# Biomass produced

```{r biomass produced}
fnms <- farm_outputs %>% 
  list.files(full.names = T) %>% 
  str_subset("biomass")

dfs <- list()
for (fid in seq_along(fnms)) {
  dfs[[fid]] <- fnms[fid] %>% 
    read_parquet() %>% 
    filter(days == max(days)) %>% 
    mutate(mean = mean %>% set_units("g") %>% set_units("t"),
           sd = sd %>% set_units("g") %>% set_units("t"))
}
df <- bind_rows(dfs)
df_mean <- df %>% 
  select(-c(days, sd)) %>% 
  pivot_wider(names_from = feed, values_from = mean) %>% 
  mutate(future_diff = (future - reference)/reference,
         past_diff = (past - reference)/reference) %>% 
  select(-c(reference, past, future)) %>% 
  pivot_longer(names_to = "feed", values_to = "mean", cols = c(future_diff, past_diff))
df_sd <- df %>% 
  select(-c(days, mean)) %>% 
  pivot_wider(names_from = feed, values_from = sd) %>% 
  mutate(future_diff = (future - reference)/reference,
         past_diff = (past - reference)/reference) %>% 
  select(-c(reference, past, future)) %>% 
  pivot_longer(names_to = "feed", values_to = "sd", cols = c(future_diff, past_diff))
df <- merge(df_mean, df_sd, by = c("farm_ID", "feed"))
```

# Locations

@@

All analysis was conducted in R version `r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

>>>>

affiliations:
  - id: 1
    name: Institute for Marine and Antarctic Studies
    group: Fisheries & Aquaculture
    address: 29 Nubeena Crescent
    city: Taroona
    region: TAS
    country: Australia
    postal-code: 7053
    url: https://www.imas.utas.edu.au/
  - id: 2
    name: Centre for Marine Socioecology
    url: https://marinesocioecology.org/
  - id: 1
    name: Institute for Marine and Antarctic Studies
    group: Ecology & Biodiversity
    # address: 29 Nubeena Crescent
    # city: Taroona
    # region: TAS
    # country: Australia
    # postal-code: 7053
    url: https://www.imas.utas.edu.au/
  # - id: 3
  #   name: Heriott-Watt University, Institute for Life and Earth Sciences
  #   department: School of Energy, Geoscience, Infrastructure and Society
  #   address: Franklin Road
  #   city: Stromness
  #   region: Orkney
  #   country: United Kingdom
  #   postal-code: KW16 3AN
  #   url: https://www.hw.ac.uk/
# keywords:
#   - keyword
#   - keyword
# abstract: |
#   Any new aquaculture venture...
# plain-language-summary: |
#   Plain language summary goes here....
# key-points:
#   - Point 1
#   - Point 2
bibliography: ["refs.bib", "manual-refs.bib"]

format: 
  html:
    theme: simplex
    css: ["extra.css"]
    code-fold: true
    code-overflow: wrap
    toc: true
    toc-expand: true
    toc-location: left
    lang: en-GB
    grid:
      sidebar-width: 350px
      body-width: 1200px
      margin-width: 250px
      gutter-width: 2em
  # pdf:
  #   papersize: a4
  #   linestretch: 1.15
  #   link-citations: true
  #   keep-tex: true
  #   template-partials:
  #     - "title.tex"
  #   include-in-header:
  #     file: "header_extra.tex"

@@

```{r setup}
#| include: false
#| eval: true
#| cache: false
#| message: false

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(dtplyr)
library(furrr)
library(RColorBrewer)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

install_unit("gfish")
install_unit("kgfish", "1000 gfish")
install_unit("tfish", "1000 kgfish")
```

@@

# Output paths
output_farm_data_path <- here() %>% file.path("outputs", "farm_data")
output_species_data_path <- here() %>% file.path("outputs", "species_data")
output_sens_data_path <- here() %>% file.path("outputs", "sensitivity_data")
output_farm_growth_data_path <- here() %>% file.path("outputs", "farm_growth_data")
output_cohort_growth_data_path <- here() %>% file.path("outputs", "cohort_growth_data")
data_analysis_path <- here() %>% file.path("outputs", "data_analysis")

@@

```{r farm info}
#| code-summary: Get general farm info

farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread() %>% 
    mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N") %>% as.factor())

farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
  rename(farm_ID = farm_id)
```

@@

```{r farm temperature data}
#| code-summary: Get the farm temperature forcings

@@

overall_mean <- mean(farm_temp_means$mean_temp)
overall_sd <- sd(farm_temp_means$mean_temp)

rm(farm_ts_data)
```

Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD).
Farms with a mean temperature of $\leq 6^\circ$C were excluded (`r as.integer(length(farms_to_omit))` farms). The total number of farms included in this analysis was therefore `r nrow(farm_temp_means)`.

```{r fig-farm-mean-temps}
#| fig-cap: |
#|   Potential options for showing farm site mean temperatures. Top left: Mean temperature by latitude across countries. Top right: Frequency distribution of mean temperatures by hemisphere. Bottom: global distribution of mean temperatures.
#| fig-height: 6
#| fig-width: 6

@@

@@

```{r fig-cohorts}
#| fig-cap: Example of cohorts
#| eval: false

@@

## Production parameters

* Salmon cohorts were always grown for 548 days
* Salmon cohorts were put out in annually Spring, on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` when farm latitude < 0 and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` when farm latitude > 0.
* Cohorts were put out every year, such that there was an annual overlap of 183 days where one cohort was nearing harvest and another was being initialised.

@@

Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as:

@@

sens_data %>% 
  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
  labs(x = "Adjusted parameter", y = "Sensitivity") +
  theme_classic() + 
  theme(legend.position = "none", 
        strip.text = element_blank(), 
        aspect.ratio = 0.8,
        text = element_text(size = 12),
        axis.title.y = element_blank()) +
  coord_flip()
```

@@

## Biomass produced

```{r biomass produced}
#| fig-cap: Modelled vs observed salmon biomass produced

coho_biom <- qs::qread(file.path(data_analysis_path, "biomass_produced_comparison.qs"))

coho_biom %>% 
  ggplot(aes(x = tonnes_per_farm, y = mean, colour = country)) +
  geom_point(size = 2.5) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  theme_classic() +
  scale_x_continuous(limits = c(0,1700)) +
  scale_y_continuous(limits = c(0,1700)) +
  scale_colour_brewer(palette = "Set1") +
  labs(y = "Modelled biomass produced (t)", x = "Observed biomass produced (t)") +
  theme_classic() +
  theme(legend.position = "top", legend.title = element_blank())
```

@@

* Main point is the difference between feeds (kg/t salmon).
* Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)

## Excreted faeces

```{r excreted faeces data}
#| code-summary: Load and prep all excretion data

fnms <- farmrun_reference_files <- file.path(output_cohort_growth_data_path) %>% 
  list.files(full.names = T)

# qs::qread(fnms[1]) %>% names()
weight <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["weight_stat"]]})
biomass <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["biomass_stat"]]})

# The following reads in all the total excretion data, pairs it with the farm coordinates, and converts the mean and sd values into values/biomass
excr_total <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["total_excr_stat"]]}) %>% 
  merge(farm_coords, by = "farm_ID") %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  mutate(sd.x = sd.x/mean.x,
         sd.y = sd.x/mean.y,
         mean.x = set_units(mean.x, "g d-1"),
         mean.y = set_units(mean.y, "gfish"),
         mean = mean.x/mean.y,
         sd_pc = sqrt(sd.x^2+sd.y^2),
         sd = sd_pc * mean,
         prod_day = case_when(hemisphere == "S" ~ t-(274+365)+1, T ~ t-(121+365)+1)) %>% 
  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))

excr_P <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["P_excr_stat"]]}) %>% 
  merge(farm_coords, by = "farm_ID") %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  mutate(sd.x = sd.x/mean.x,
         sd.y = sd.x/mean.y,
         mean.x = set_units(mean.x, "g d-1"),
         mean.y = set_units(mean.y, "gfish"),
         mean = mean.x/mean.y,
         sd_pc = sqrt(sd.x^2+sd.y^2),
         sd = sd_pc * mean) %>% 
  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))

excr_L <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["L_excr_stat"]]}) %>% 
  merge(farm_coords, by = "farm_ID") %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  mutate(sd.x = sd.x/mean.x,
         sd.y = sd.x/mean.y,
         mean.x = set_units(mean.x, "g d-1"),
         mean.y = set_units(mean.y, "gfish"),
         mean = mean.x/mean.y,
         sd_pc = sqrt(sd.x^2+sd.y^2),
         sd = sd_pc * mean) %>% 
  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))

excr_C <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["C_excr_stat"]]}) %>% 
  merge(farm_coords, by = "farm_ID") %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  mutate(sd.x = sd.x/mean.x,
         sd.y = sd.x/mean.y,
         mean.x = set_units(mean.x, "g d-1"),
         mean.y = set_units(mean.y, "gfish"),
         mean = mean.x/mean.y,
         sd_pc = sqrt(sd.x^2+sd.y^2),
         sd = sd_pc * mean) %>% 
  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
```

### Total amount

```{r fig-total-excr-diff_perc, class.chunk = "aside"}
#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) with increasing overall excretion.

df <- excr_total %>% 
  select(-c(sd, sd_pc)) %>% 
  pivot_wider(names_from = "feed", values_from = "mean") %>% 
  mutate(past = past-reference,
         future = future-reference) %>% 
  pivot_longer(names_to = "feed", values_to = "diff", cols = c(past, future), names_transform = list(feed = as.factor)) %>% 
  mutate(reference = set_units(reference, "g kgfish-1 d-1"),
         diff_perc = drop_units(diff/reference))

summ <- df %>%
  group_by(hemisphere, feed) %>% 
  reframe(mean = 100*meanna(diff_perc) %>% round(3),
          min = 100*meanna(diff_perc) %>% round(3),
          max = 100*maxna(diff_perc) %>% round(3))

df %>% 
  ggplot(aes(x = reference, y = diff_perc, colour = hemisphere)) +
  geom_point() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  theme_classic()
```

There was very little variation in the percentage difference (from reference) excreted with increasing overall excretion (@fig-total-excr-diff_perc), or through time (@fig-total-excr-diff_perc_2). 
The difference in total excretion for the past feed ranged from 
`r summ$min[summ$feed == "past"]`-`r summ$max[summ$feed == "past"]`% across all farms globally, and for the future feed ranged from 
`r summ$min[summ$feed == "future"]`-`r summ$max[summ$feed == "future"]`%.

```{r fig-total-excr-diff_perc_2, class.chunk = "aside"}
#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.

df %>% 
  group_by(prod_day, feed, hemisphere) %>% 
  reframe(diff_perc_mean = meanna(diff_perc),
          diff_perc_sd = sdna(diff_perc)) %>% 
  ggplot(aes(x = prod_day, y = diff_perc_mean, ymin = diff_perc_mean-diff_perc_sd, ymax = diff_perc_mean+diff_perc_sd, 
             colour = as.factor(hemisphere), fill = as.factor(hemisphere))) +
  geom_line() + 
  geom_ribbon(alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  theme_classic()
```

However, the actual difference in excreted faeces varied by feed, time in the production cycle, and location of the farm [@fig-total-excr-act_diff].

```{r fig-total-excr-act_diff}
#| fig-width: 6.25
#| fig-height: 5.25
#| fig-cap: Mean actual difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.

df <- excr_total %>% 
  select(-c(sd, sd_pc)) %>% 
  pivot_wider(names_from = "feed", values_from = "mean") %>% 
  mutate(past = past-reference,
         future = future-reference) %>% 
  pivot_longer(names_to = "feed", values_to = "diff", cols = c(past, future), names_transform = list(feed = as.factor)) %>% 
  mutate(reference = set_units(reference, "g kgfish-1 d-1"),
         diff = set_units(diff, "kg tfish-1 d-1"))

summ <- df %>%
  group_by(hemisphere, feed) %>% 
  reframe(mean = meanna(diff) %>% round(3),
          min = meanna(diff) %>% round(3),
          max = maxna(diff) %>% round(3))

df %>% 
  group_by(hemisphere, feed, prod_day) %>% 
  reframe(mean_diff = meanna(diff),
          sd_diff = sdna(diff) %>% set_units("kg tfish-1 d-1")) %>% 
  ggplot(aes(x = prod_day, y = mean_diff, ymin = mean_diff-sd_diff, ymax = mean_diff+sd_diff, colour = hemisphere, fill = hemisphere)) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(~feed) +
  theme_classic()
```

## Uneaten feed (amount & composition)

## Total nutrients (amount & source)

```{r patchwork map}
worldmap <- ne_countries(scale = "large", returnclass = "sf")

AUS_bounds <- c(144, 149.5, -39.75, -44)
CAN1_bounds <- c(-132, -122, 47.75, 54.25)
CAN2_bounds <- c(-70, -54, 43, 48.5)
CHI_bounds <- c(-77.5, -62.5, -56, -25)
EUR_bounds <- c(-26, 30, 51, 71)

p_ALL <- ggplot(data = worldmap, aes(geometry = geometry)) +
  geom_sf(fill = "white", color = "dimgray") +
  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
  coord_sf() +
  theme_classic()

no_margins <- function() {
  theme(legend.position = "none", 
        plot.margin = margin(),
        axis.title = element_blank())
}

p_Aus <- p_ALL + coord_sf(xlim = AUS_bounds[1:2], ylim = AUS_bounds[3:4], expand = FALSE) + no_margins()
p_Eur <- p_ALL + coord_sf(xlim = EUR_bounds[1:2], ylim = EUR_bounds[3:4], expand = FALSE) + no_margins()
p_Chi <- p_ALL + coord_sf(xlim = CHI_bounds[1:2], ylim = CHI_bounds[3:4], expand = FALSE) + no_margins()
p_Can <- p_ALL + coord_sf(xlim = CAN1_bounds[1:2], ylim = CAN1_bounds[3:4], expand = FALSE) + no_margins()
p_USA <- p_ALL + coord_sf(xlim = CAN2_bounds[1:2], ylim = CAN2_bounds[3:4], expand = FALSE) + no_margins()

subplot <- (p_Eur/p_Aus) + plot_layout(heights = c(1.5, 1))
finalplot <- (p_Can + p_USA) / (p_Chi + subplot) + 
  plot_layout(widths = c(1, 1.5), heights = c(1, 2)) &
  theme(plot.margin = margin(0, 0, 0, 0))
finalplot
```

@@

All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
Major packages used include terra [@terra], targets [@targets], future [@future], furrr [@furrr], and the tidyverse [@tidyverse].
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
